---
title: "report"
author: "Joy Polk"
format: html
editor: visual
---

## Introduction

This section will introduce the research problem, purpose, and research question(s).

## Data

This section will describe the data source, sample, variables, and any data preparation process.

## Methods

This section will describe the statistical methods and analytic procedures used to address the research question(s).

## Results

This section will present the results of the analysis, including relevant estimates, tables, and figures.

```{r}

x <- 0:10
mean(x)
```

The results from the analysis will be interpreted and summarized here.

## Reproducibility

To asses the portability of the project, I cloned the GitHub repository and rendered `report.qmd` on a second computer running Windows 11 x64 with R version 4.5.3. The report rendered successfully from the fresh clone without requiring any changes to the repository or project files. The `sessionInfo()` output below reports the R environment for the machine on which the report is currently rendered.

```{r}

sessionInfo()
```
